\documentclass[10pt]{cv}
\usepackage{natbib}
\usepackage{etaremune}
\usepackage{fancyhdr}


\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
            
\font\cap=cmcsc10
 
\topmargin 0pt
\headheight 0pt
\headsep 0pt
\textheight 9in
\parindent 0pt
\parskip \baselineskip
\topmargin 0in
\oddsidemargin -0.25in
\evensidemargin -0.25in

\textwidth 6.9in

\setlength{\topmargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\topskip}{0.4in}
\setlength{\textheight}{9.3in}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\lfoot{Rocio Kiman}
\cfoot{\thepage}
\rfoot{Curriculum Vitae}
\newcommand\tab[1][1cm]{\hspace*{#1}}

\hypersetup{colorlinks = true} %comment out for any printed version! 

%footer options:
\setcounter{page}{1} %set the number in the second set of curly braces to the number that would be on the first page
\newcommand{\secondfooter}{Publications} %the footer you'd like on the publications half should be uncommented
%\newcommand{\secondfooter}{Curriculum Vitae} 
\newcommand{\firstpagestyle}{empty} %the style of the first page: fancy = include footer, empty = don't.
%\newcommand{\firstpagestyle}{fancy}

\begin{document}
\thispagestyle{\firstpagestyle} 
\begin{center}
{\LARGE \textbf{\sc Rocio Kiman}}\\
\bigskip
\bigskip
%\smallskip
\end{center}
\normalsize
  
\addresses
{
Citizenship: Argentina and Spanish\\
Email: rociokiman@gmail.com\\
Website: \href{https://rkiman.github.io}{rkiman.github.io}\\
Last updated: October 30 2023\\
}
{
California Institute of Technology\\
1200 E California Blvd\\
Pasadena, California 91125
}

\begin{llist}

\sectiontitle{Appointments}

\textbf{Sherman Fairchild Postdoctoral Scholar\\Research Associate in Astronomy}
\location{September 2022--Present}
California Institute of Technology \\
Pasadena, California, USA.

\textbf{Volunteer for Astronomy Outreach}
\location{July 2022}
Santa Barbara Museum of Natural History \\
Santa Barbara, California, USA.


\textbf{Postdoctoral Scholar}
\location{September 2021--August 2022}
Kavli Institute for Theoretical Physics \\
University of California, Santa Barbara \\
Santa Barbara, California, USA.


\sectiontitle{Education}
\textbf{The Graduate Center, City University of New York}
\location{2016--2021}
Ph.D. in Physics\\
Master of Philosophy Physics (June 2, 2020)\\
Thesis Title: ``A Unified Approach to M Dwarf Ages''\\
Thesis Advisors: Prof. Kelle Cruz \& Dr. Jackie Faherty \\
New York, New York, USA.

\textbf{Universidad de Buenos Aires}
\location{2011--2016}
Licenciatura in Physics\\
Thesis Title: ``Higgs boson pair production at the LHC''\\
Thesis Advisor: Prof. Daniel de Florian\\
Buenos Aires, Argentina.



\sectiontitle{Grants \&\\ Awards}

TESS Cycle 5 Guest Investigator Program, for \$$70,000$
\location{July 19 2022}
PSC-CUNY Cycle 51 Trad B Research Award, (PI: K.Cruz) for \$$6000$
\location{April 16 2020}
Sigma Xi Grants in Aid of Research, for \$$4334$
\location{June 01 2019}
Doctoral Student Research Grant (Round 14) for \$$875$    
\location{March 13 2019}
Provost’s Pre-Dissertation Research Fellowship for the Sciences, for \$$5000$
\location{March 08 2019}
K2 Guest Observer Cycle 6 (PI: J. Faherty) for \$$125,000$
\location{Junes 25 2018}
PSC-CUNY Cycle 49 Trad B Research Award (PI: K.Cruz) for \$$6000.00$
\location{April 13 2018}
CUNY Science Scholarship
\location{August 25 2016}
\tab AY 2016–2017: \$$26,000$ stipend and full tuition\\
\tab AY 2017–2018, AY 2018–2019, AY 2019–2020\\ 
\tab and AY 2020–2021: full tuition\\
CONICET Doctoral Fellowship, \$$5270$ stipend
\location{April 01--August 24 2016}


\sectiontitle{Open source\\code and\\tutorials}

\texttt{wdwarfdate}: Open source code that estimates ages of white dwarfs in a Bayesian framework. [\href{https://github.com/rkiman/wdwarfdate}{Source}] [\href{https://wdwarfdate.readthedocs.io/en/latest/}{Docs}] \\
\textbf{Modeling 1: Make a quick fit using astropy.modeling}
Astropy Python Package tutorial. [\href{http://learn.astropy.org/rst-tutorials/Models-Quick-Fit.html?highlight=filtertutorials}{Docs}]\\
\textbf{Modeling 2: Create a User Defined Models using astropy.modeling}
Astropy Python Package tutorial. [\href{http://learn.astropy.org/rst-tutorials/User-Defined-Model.html?highlight=filtertutorials}{Docs}] 

\sectiontitle{Observing\\Time\\Awarded}

Three nights with the Double Spectrograph (DBSP), Palomar Observatory for the 2023A semester (PI: R. Kiman).\\
Three nights with the Double Spectrograph (DBSP), Palomar Observatory for the 2022B semester (PI: G. Hallinan).


\sectiontitle{Invited Talks}

Seminar Center for Astrophysics, Harvard University, October 18 2022, \textit{Studying Radius Inflation on Low-Mass Stars Using Gaia DR3.}\\
Seminar at IPAC/Caltech, October 5 2022, \textit{A Unified Approach to M Dwarf Ages.}\\
Kavli Institute for Theoretical Physics, Probes of Transport in Stars Program, December 9 2021, \textit{Through the Fully Convective Boundary: An Overview of Low-mass Stars and Brown Dwarfs.}\\
Berkeley online short talk, April 22 2021, \textit{Age Relations for Low-Mass Stars.}\\
Carnegie Observatories online Lunch Talk, March 19 2021, \textit{Age Relations for Low-Mass Stars.}\\
Center for Astrophysics's Exoplanet Presentation Lounge online, February 23 2021, \textit{Age Relations for Low-Mass Stars.}\\ 
Gemini Observatory Seminar, January 10 2020, Hilo, HI, USA. \textit{Age-dating low mass stars using magnetic activity and kinematics.}\\
Leibniz-Institut f\"{u}r Astrophysik Potsdam (AIP) Seminar, July 2 2019, Potsdam, Germany. \textit{Finding Age Relations for Low Mass Stars Using Magnetic Activity and Kinematics.}\\
Princeton University Seminar, May 23 2019, NJ, USA. \textit{Finding Age Relations for Low Mass Stars Using Magnetic Activity and Kinematics.} \\
Invited panelist, AAS 233, 6--10 January, 2019, Seattle, Washington, USA. \textit{An Open Discussion on Software.} 

\sectiontitle{Selected\\Contributed\\Presentations}

Contributed talk, American Astronomical Society Meeting \#241, 8-12 January 2023, Seattle, Washington, \textit{Studying Radius Inflation on Low-Mass Stars Using Gaia DR3}.\\
Fifty Years of the Skumanich Relations, March 08-11 2022, Boulder, Colorado USA, \textit{A unified approach to M dwarf ages.}\\
University of Washington online Lunch Talk, March 9 2021, \textit{Age Relations for Low-Mass Stars.}\\
Leiden Observatory online Lunch Talk, February 2 2021, \textit{Age Relations for Low-Mass Stars.}\\
Dartmouth online Journal club, September 9 2020, \textit{Age Relations for Low-Mass Stars.}\\
Poster presentation, American Astronomical Society Meeting \#235, 4-8 January, 2020, Honolulu, HI, USA. \textit{Age-Activity relation for M dwarfs using H$\alpha$ equivalent widths} Kiman R., Faherty J., Cruz K., Xu S., Schmidt S., Angus R., Gagn\'e J., Bardalez Gagliuffi D., Rice E.\\
Contributed talk, TRAPPIST-1 conference, June 11--14, 2019, Li\`ege, Belgium. \textit{TRAPPIST-1 in the context of M-dwarfs re-defined by Gaia DR2.}\\
Contributed talk, Big Apple Magnetic Fields Conference, January 24--25, 2019, Center for Computational Astrophysics at the Flatiron Institute, NY, New York, USA. \textit{Finding age relations for low mass stars using magnetic activity and kinematics.}\\
Poster presentation, American Astronomical Society Meeting \#233, 6--10 January, 2019, Seattle, Washington, USA. \textit{Finding age relations for low mass stars using magnetic activity and kinematics.} Kiman, R., Schmidt, S.J., Angus, R., Cruz, K.L., Faherty, J.K. \& Rice, E.\\
Poster presentation, Cool Stars, July 30 to August 3, 2018, Boston-Cambridge, USA. \textit{Age Dating Low Mass Stars Using Galactic Kinematics.} Kiman, R., Schmidt, S.J., Angus, R., Cruz, K.L., Faherty, J.K. \& Rice, E.\\
Contributed talk, Cool Stars, July 30 to August 3, 2018, Boston-Cambridge, USA. \textit{Age Dating Low Mass Stars Using Galactic Kinematics.} \\
%Contributed talk, Graduate Research Conference, May 10, 2018, College of Staten Island, NY, USA. \textit{Age Dating Low Mass Stars Using Galactic Kinematics.}\\
%Poster presentation, AAS 231, 8--12 January, 2018, Washington DC, USA. \textit{Age Dating Low Mass Stars Using Galactic Kinematics.} Kiman, R., Cruz, K.L., Angus, R., Schmidt, S.J. \& Faherty, J.K\\
%Poster presentation, BDExoCon II, 26--27 October 2017, Delaware, USA. \textit{Gaia-Cupid: Age-dating low mass stars using galactic kinematics.} Kiman, R., Cruz, K.L, Angus, R., Schmidt, S.J \& Faherty, J.K.\\
%Lightning Talk, SDSS-IV Collaboration Meeting, 24--26 July 2017, Santiago, Chile. \textit{Gaia-Cupid: Age-dating low mass stars using galactic kinematics.} \\
%Poster Presentation, 99º RNF-AFA (National Meeting of the Physical Association Argentina) 22--25 September, 2014, Buenos Aires, Argentina. \textit{Photolysis of caged compounds with controlled temporal modulation.} Kiman, R., Camino, P., Ponce Dawson, S., Lopez, L., Piegari, S.

\sectiontitle{Schools and\\Selected\\Conferences\\Attended}
\textit{LSST program} September 8--13 2019, CCA, New York\\
\textit{Space Astrometry For Astrophysics.} 3--7 June 2019, L'Aquila, Italy\\
\textit{.Astronomy X.} 24--27 September 2018, Baltimore MD, USA.\\
\textit{Gaia Sprint.} 4--8 to June, 2018, Center for Computational Astrophysics at the Flatiron Institute, NY, New York, USA.\\
\textit{Python in Astronomy.}  April 30 to May 4, 2018, Center for Computational Astrophysics at the Flatiron Institute, NY, New York, USA. \\
\textit{Gaia DR2 Sprint.} 25--27 April, 2018, Center for Computational Astrophysics at the Flatiron Institute, NY, New York, USA. \\
\textit{IYAS on the scientific exploration of the Gaia data.} February 26 to March 2, 2018, Paris, France.\\
\textit{La Serena School of Data Science.} 21-29 August, 2017, La Serena, Chile.


\sectiontitle{Teaching\\Experience}

ASTRO 10200 - Laboratory Explorations in Astronomy
\location{2019--2020}
Hunter College, CUNY, New York, USA\\
Classical Mechanics, University of Buenos Aires, Argentina
\location{2016} 
Private Tutor for High-School and Undergraduate Students
\location{2009--2015}
High-school subjects: Mathematics, Physics, Chemistry and Informatic\\
Undergraduate subjects: Calculus, Algebra, Physics and Chemistry 

\sectiontitle{Outreach\\Activities}

Solar annular eclipse viewing from Bryce Canyon National Park, with star party at night. October 14 2023. Bryce Canyon National Park, Utah.  \\
Astronomy on Tap talk: \textit{The evolution of the stars.} October 11 2023. Grand Canyon Lodge, North Rim, Arizona.\\
Spanish Language Stargazing Lecture: \textit{Cu\'al es la edad de una estrella?} August 18 2023. CalTech, Pasadena, California. \\
Help organization and participate on International Astronomy day at Santa Barbara, together with the Santa Barbara Museum of Natural History and the Astronomical Unit. April 29 2023. Santa Barbara, California.\\
Participation on Pasadena School Science Fair, solar observation with H$\alpha$ telescope. April 22 2023. Pasadena, California. \\
Astronomy on Tap talk: \textit{How old are stars?} February 13 2023. Pasadena, California.\\
Participation in the explaining video about JWST with the Santa Barbara Museum of Natural History. July 13 2022. Available \href{https://www.youtube.com/watch?v=LV8N0OSEJOg}{online}.\\
Planetarium presentations: \textit{Explorando el Sistema Solar.} Santa Barbara Museum of Natural History, Sundays during July 2022. Santa Barbara, California. \\
Invited talk about the Lunar Eclipse for the Astronomy Girl Scouts Club, at the Santa Barbara Museum of Natural History, May 13 2022. Santa Barbara, California. \\
Invited talk at the Graduate Student Research Symposium, October 23 2020. City College of New York, CUNY.	\\
Public talk at \textit{Viernes Astron\'omicos: Cu\'al es la edad de las estrellas?}, September 18 2020. Universidad Nacional Mayor de San Marcos, Lima, Per\'u. Open public. Available \href{https://www.youtube.com/watch?v=QOlgG1b41hU&ab_channel=AstronomySanMarcos}{online}.\\
Participation in the presentation in Spanish, September 24 2019. \textit{Astronom\'ia en Vivo: Historia del Universo}. American Museum of Natural History, New York, USA. Open public.\\
Presentation at Adventures in Science Camps, January 29 2019. American Museum of Natural History, New York, USA. For children in Grades 1--5.\\
Outreach Assistant, 2014--2016. Universidad de Buenos Aires, Argentina\\
\tab Presenter at the ``Physics week'' for high-school students, 2014-2015.\\
\tab Presenter at the ``­Museum's night'', 2014-2015.\\
\tab Presenter at the Book Fair in Buenos Aires, May 2015.\\
\tab Monthly outreach talks for high-school students about the career in Physics.

\sectiontitle{Observing\\experience}

Three nights with the Double Spectrograph (DBSP), 
\location{Spring semester 2023}
Palomar Observatory \\
Three nights with the Double Spectrograph (DBSP), 
\location{Fall semester 2022}
Palomar Observatory \\
FIRE at the Magellan Telescope at Las Campanas Observatory
\location{December 10--13 2019}
 in Chile. For the Backyard worlds project. \\
SpeX at the NASA Infrared Telescope Facility (NASA IRTF) 	
\location{August 28 2018}
Telescope at the Mauna Kea Observatory in Hawaii. Remote Observing. \\
CAPSCam at the DuPont Telescope	
\location{November 30 2017}
at Carnegie's Las Campanas Observatory in Chile. Remote Observing.



\sectiontitle{First Author\\Publications}

\begin{etaremune}
  \item Measuring Radii of Single FGK and M Dwarfs Using Gaia~DR3 to Study the Effect of Magnetic Activity.\\ \textbf{Kiman, R.}; Brandt, T. D.; Faherty, J. K.; Popinchalk, M.; in prep.
  \item \href{https://ui.adsabs.harvard.edu/abs/2022AJ....164...62K/abstract}{\texttt{wdwarfdate}: A Python Package to Derive Bayesian Ages of White Dwarfs.}\\ \textbf{Kiman, R.},; Xu, S.; Faherty, J.K.; Angus, R.; Brandt, T.D.; Casewell, S.L., Gagn\'e; J., Cruz, K.L.; The Astronomical Journal, 164, 2, 13 (2022) DOI: 10.3847/1538-3881/ac7788
  \item \href{https://ui.adsabs.harvard.edu/abs/2021AJ....161..277K/abstract}{Calibration of the ${\rm H}\alpha$ Age-Activity relation for M dwarfs}\\ \textbf{Kiman, R.}; Faherty, J.K.; Cruz, K.L.; Gagn\'e , J.; Angus, R.; Schmidt, S. J.; Mann, A.W.; Bardalez Gagliuffi, D.C.; Rice, E.; The Astronomical Journal, 161, 6, 22 (2021) DOI: 10.3847/1538-3881/abf561
  \item \href{https://ui.adsabs.harvard.edu/abs/2019AJ....157..231K/abstract}{Exploring the age dependent properties of M and L dwarfs using \textit{Gaia} and SDSS.}\\ \textbf{Kiman, R.}, Schmidt, S.J., Angus, R., Cruz, K.L., Faherty, J.K. \& Rice, E., The Astronomical Journal, 157, 6, 231 (2019) DOI: 10.3847/1538-3881/ab1753 
\end{etaremune}





\sectiontitle{Co-author\\Publications}
\begin{etaremune}

 \item \href{https://ui.adsabs.harvard.edu/abs/2023MNRAS.524..695Z/abstract}{Dynamical masses and ages of Sirius-like systems} \\ Zhang, H.; Brandt, T. D. ; \textbf{Kiman, R.}; Venner, A.; An, Q.; Chen, M.; Li, Y.; Monthly Notices of the Royal Astronomical Society, 524, 1, 695-715 (2023) DOI: 10.1093/mnras/stad1849

 \item \href{https://ui.adsabs.harvard.edu/abs/2023MNRAS.522.5622L/abstract}{Surveying nearby brown dwarfs with HGCA: direct imaging discovery of a faint, high-mass brown dwarf orbiting HD 176535 A} \\ Li, Y.; Brandt, T. D.; Brandt, G. M.; An, Q.; Franson, K.; Dupuy, T. J.; Chen, M.; Bowens-Rubin, R.; Lewis, B. L.; Bowler, B. P.; Gibbs, A.; \textbf{Kiman, R.}; Faherty, J. K.; Currie, T.; Jensen-Clem, R.; Zhang, H.; Contreras-Martinez, E.; Fitzgerald, M. P. ; Mazin, B. A.; Millar-Blanchaer, M.; Monthly Notices of the Royal Astronomical Society, 522, 4, 622-5637 (2023) DOI: 10.1093/mnras/stad1315

 \item \href{https://ui.adsabs.harvard.edu/abs/2023ApJ...945..119G/abstract}{The Oceanus Moving Group: A New 500 Myr Old Host for the Nearest Brown Dwarf} \\ Gagn\'e, J.; Moranta, L.; Faherty, J. K.; \textbf{Kiman, R.}; Couture, D.; Larochelle, A. R.; Popinchalk, M.; Morrone, D.; The Astrophysical Journal, 945, 2, 23 (2023) DOI: 10.3847/1538-4357/acb8b7

  \item \href{https://ui.adsabs.harvard.edu/abs/2023ApJ...945..114P/abstract}{Examining the Rotation Period Distribution of the 40 Myr Tucana-Horologium Association with TESS} \\ Popinchalk, M.; Faherty, J. K.; Curtis, J. L.; Gagn\'e, Jonathan; Bardalez Gagliuffi, D. C.; Vos, J. M.; Ayala, A.; Gonzales, L.; \textbf{Kiman, R.}; The Astrophysical Journal, 945, 2, 18 (2023) DOI: 10.3847/1538-4357/acb055

  \item \href{https://ui.adsabs.harvard.edu/abs/2022MNRAS.tmp.2758E/abstract}{Magnetic braking saturates: evidence from the orbital period distribution of low-mass detached eclipsing binaries from ZTF}\\ El-Badry, K.; Conroy, C.; Fuller, J.; \textbf{Kiman, R.}; van Roestel, J.; Rodriguez, A. C.; Burdge, K. B.; Monthly Notices of the Royal Astronomical Society, Advance Access (2022) DOI: 10.1093/mnras/stac2945
  
  \item \href{https://ui.adsabs.harvard.edu/abs/2022AJ....164...33C/abstract}{The POKEMON Speckle Survey of Nearby M Dwarfs. I. New Discoveries}\\ Clark, C. A.; van Belle, G. T.; Horch, E. P.; von Braun, K.; Ciardi, D. R.; Winters, J. G.; \textbf{Kiman, R.}; The Astronomical Journal, 164, 2, 13 (2022) DOI: 10.3847/1538-3881/ac739c 
  
  \item \href{https://ui.adsabs.harvard.edu/abs/2022AJ....164....3K/abstract}{Discovery of 34 Low-mass Comoving Systems Using NOIRLab Source Catalog DR2}\\ Kiwy, F.; Faherty, J. K.; Meisner, A.; Schneider, A. C.; Kirkpatrick, J. D.; Kuchner, M. J.; Burgasser, A. J.; Casewell, S.; \textbf{Kiman, R.}; Calamari, E.; Aganze, C.; Hsu, C.; Sainio, A.; Thakur, V.; Backyard Worlds: Planet 9 Collaboration; The Astronomical Journal, 164, 1, 24 (2022) DOI: 10.3847/1538-3881/ac68e7

  \item \href{https://ui.adsabs.harvard.edu/abs/2022RNAAS...6..127B/abstract}{WDJ220838.73+454434.04: a White Dwarf Companion in the AR Lacertae System}\\ Bickle, T. P.; Jalowiczor, P. A.; Casewell, S. L.; Faherty, J. K.; \textbf{Kiman, R.}; Schneider, A. C. ; Kirkpatrick, J. D.; Meisner, A. M.; Kuchner, M. J.; Caselden, D.; Backyard Worlds: Planet 9 Collaboration; Research Notes of the AAS, 6, 6, 127 (2022). DOI: 10.3847/2515-5172/ac780a

  \item \href{https://ui.adsabs.harvard.edu/abs/2021arXiv210805321S/abstract}{Ross 19B: An Extremely Cold Companion Discovered via the Backyard Worlds: Planet 9 Citizen Science Project}\\ Schneider, A. C. ; Meisner, A. M. ; Gagne, J. ; Faherty, J. K. ; Marocco, F. ; Burgasser, A. J. ; Kirkpatrick, J. D. ; Kuchner, M. J. ; Gramaize, L. ; Rothermich, A. ; Brooks, H. ; Vrba, F. J. ; Bardalez Gagliuffi, D. ; Caselden, D. ; Cushing, M. C. ; Gelino, C. R. ; Line, M. R. ; Casewell, S. L. ; Debes, J. H. ; Aganze, C.; Ayala, A. ; Gerasimov, R. ; Gonzales, E. C. ; Hau, C. ; \textbf{Kiman, R.} ; Popinchalk, M. ; Theissen, C. ; The Backyard Worlds; Planet 9 Collaboration; The Astrophysical Journal, 921, 2, 13 (2021) DOI: 10.3847/1538-4357/ac1c75

  \item \href{https://ui.adsabs.harvard.edu/abs/2021ApJ...916...77P/abstract}{Evaluating Rotation Periods of M dwarfs}\\ Popinchalk, M.; Faherty, J.; \textbf{Kiman, R.}; Angus, R.; Curtis, J.; Gagne, J.; Cruz, K.; Rice, E.; The Astrophysical Journal, 916, 2, 77 (2021) DOI:  10.3847/1538-4357/ac0444

  \item \href{https://ui.adsabs.harvard.edu/abs/2021arXiv210201772Y/abstract}{Gyro-Kinematic Ages for $29,949$ Kepler Stars}\\ Lu, Y.; Angus, R.; Curtis, J.L.; David, T.J., \textbf{​Kiman, R.}​; The Astronomical Journal, 161,  4, 189 (2021) DOI: 10.3847/1538-3881/abe4d6

  \item \href{https://ui.adsabs.harvard.edu/abs/2021ApJS..253....7K/abstract}{The Field Substellar Mass Function Based on the Full-sky 20-pc Census of 525 L, T, and Y Dwarfs.}\\ Kirkpatrick, J.D.; Gelino, C.R.; Faherty, J.K.; Meisner, A.M.; Caselden, D.; Schneider, A.C.; Marocco, F.; Cayago, A.J.; Smart, R.L.; Eisenhardt, P.R.; Kuchner, M.J.; Wright, E.L.; Cushing, M.C.; Allers, K.N.; Bardalez Gagliuffi, D.C.; Burgasser, A.J.; Gagne, J.; Logsdon, S.E.; Martin, E.C.; Ingalls, J.G.; Lowrance, P.J.; Abrahams, E.S.; Aganze, C.; Gerasimov, R.; Gonzales, E.C.; Hsu, C.; Kamraj, N.; \textbf{​Kiman, R.}​; et al, The Astrophysical Journal Supplement Series, 253, 1, 85 (2021) DOI: 10.3847/1538-4365/abd107

  \item \href{https://ui.adsabs.harvard.edu/abs/2020AJ....160..156S/abstract}{Discovery of a Nearby Young Brown Dwarf Disk}\\ Schutte, M. C.; Lawson, K. D.; Wisniewski, J. P.; Kuchner, M. J.; Silverberg, S. M.; Faherty, J. K.; Bardalez Gagliuffi, D. C.; \textbf{Kiman, R.}; Gagné, J.; Meisner, A.; Schneider, A. C.; Bans, A. S.; Debes, J. H.; Kovacevic, N.; Bosch, M. K. D.; Durantini Luca, H. A.; Holden, J.; Hyogo, M.; The Astronomical Journal, 160, 4, 10 (2020) DOI: 10.3847/1538-3881/abaccd 

  \item \href{https://ui.adsabs.harvard.edu/abs/2020ApJ...899..123M/abstract}{Spitzer Follow-up of Extremely Cold Brown Dwarfs Discovered by the Backyard Worlds: Planet 9 Citizen Science Project.}\\ Meisner, A. M.; Faherty, J.K.; Kirkpatrick, J. D.; Schneider, A.C.; Caselden, D.; Gagné, J.; Kuchner, M.J.; Burgasser, A.J.; Casewell, S.L.; Debes, J.H.; Artigau, É.; Bardalez Gagliuffi, D.C.; Logsdon, S.E.; \textbf{Kiman, R.} et al., The Astrophysical Journal, Volume 899, Issue 2, id.123 (2020) DOI:10.3847/1538-4357/aba633

  \item \href{https://ui.adsabs.harvard.edu/abs/2020AJ....160...90A/abstract}{Exploring the evolution of stellar rotation using Galactic kinematics}\\ Angus, R.; Beane, A.; Price-Whelan, A. M.; Newton, E.; Curtis, J. L.; Berger, T.; van Saders, J.; \textbf{Kiman, R.}; Foreman-Mackey, D.; Lu, Y.; Anderson, L.; Faherty, J. K., The Astronomical Journal, Volume 160, Number 2 (2020) DOI: 10.3847/1538-3881/ab91b2

  \item \href{https://ui.adsabs.harvard.edu/abs/2019AJ....158..173A/abstract}{Toward Precise Stellar Ages: Combining Isochrone Fitting with Empirical Gyrochronology.}\\  Angus, R., Morton, T. D., Foreman-Mackey, D., van Saders, J., Curtis, J., Kane, S. R., Bedell, M., \textbf{Kiman, R.}, Hogg, D. W.; Brewer, J. The Astronomical Journal, Volume 158, Issue 5, article id. 173, 12 pp. (2019). DOI: 10.3847/1538-3881/ab3c53
\end{etaremune}


\end{llist}
\end{document}